Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Weight and Convex Input Constraints

### 2025-04-16 manuscript.tex
correct figure
exp. set upload

% ------------------------------------
% Real-time Implementation Set-up
% ------------------------------------
\begin{figure}[t]
    \centering
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            fig/exp_set.jpg
        }%
    \caption{
        Robot setup for the real-time experiment.
    }
    \label{fig:ctrl:exp:set}
  \end{figure}

@@

% ------------------------------------
% Robot Model Figure and Table
% ------------------------------------
\begin{figure}[t]
    \centering
    \subfloat[Two-link manipulator model.]{
        \includegraphics[width=0.75\linewidth]{src/figures/RobotModel.drawio.pdf}
        \label{fig:robot:model}
    }
    \hfill
    \subfloat[Control input saturation function.\MSRY{sat이 아니라 집합으로 표현하기}]{
        \includegraphics[width=0.45\linewidth]{src/figures/saturation.drawio.pdf}
        \label{fig:robot:sat}
    }
    \caption{Two-link manipulator model and control saturation function.}
    \label{fig:robot}
\end{figure}

>>>>

% ------------------------------------
% Real-time Implementation Set-up
% ------------------------------------
\begin{figure}[t]
    \centering
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/figures/exp_set.drawio.png
        }%
    \caption{
        Robot setup for the real-time experiment.
    }
    \label{fig:ctrl:exp:set}
\end{figure}

@@

% ------------------------------------
% Robot Model Figure and Table
% ------------------------------------
\begin{figure}[t]
    \centering
    \subfloat[Two-link manipulator model.]{
        \includegraphics[width=0.75\linewidth]{src/figures/RobotModel.drawio.pdf}
        \label{fig:robot:model}
    }
    \hfill
    \subfloat[Control input saturation function.]{
        \includegraphics[width=0.55\linewidth]{src/figures/saturation.drawio.pdf}
        \label{fig:robot:sat}
    }
    \caption{Two-link manipulator model and control saturation function.}
    \label{fig:robot}
\end{figure}
